### 2016-01-19 paper.tex
Remove 'we also see'
Thanks --> due

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade
tip vortex shedding are relatively weaker, which is likely an effect of the
RM2's lower solidity and tapered blades.

@@

Weighted averages for the transport terms in the mean kinetic energy
equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport thanks
to the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though a detailed anaylsis of the
downstream evolution and turbine interaction will be necessary.

>>>>

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is relatively
weaker, which is likely an effect of the RM2's smaller blade chord length and
tapered blades.

@@

Weighted averages for the transport terms in the mean kinetic energy
equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport due to
the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though a detailed anaylsis of the
downstream evolution and turbine interaction will be necessary.
